The 2- and 3-point surface correlation functions calculations: from novel exact continuous approach to improving methodology for discrete images

### 2023-05-17 paper.tex
Major -> basic

The rest of the manuscript is organized as follows: in \cref{sec:def} we
introduce some major definitions of CFs necessary for establishing algorithms,
in \cref{sec:algo} we describe the all methodological details for "discrete"
method for digital images. Next, in \cref{sec:algo-precise} we explain in detail
why verification of computational approaches for digital images is currently
hampered, and then introduce novel exact "continuous" methodology in
\cref{sec:fss-2d}. The choice of verification cases is presented in
\cref{sec:results} followed by improvements in methodology of Samarin et~al. The
paper concludes with discussion, outline and summary in \cref{sec:summary}.

>>>>

The rest of the manuscript is organized as follows: in \cref{sec:def} we
introduce some basic definitions of CFs necessary for establishing algorithms,
in \cref{sec:algo} we describe the all methodological details for "discrete"
method for digital images. Next, in \cref{sec:algo-precise} we explain in detail
why verification of computational approaches for digital images is currently
hampered, and then introduce novel exact "continuous" methodology in
\cref{sec:fss-2d}. The choice of verification cases is presented in
\cref{sec:results} followed by improvements in methodology of Samarin et~al. The
paper concludes with discussion, outline and summary in \cref{sec:summary}.
